---
title: "Data Wrangling"
date: "May 02, 2020"
output: html_document
---


# Example

To explore the basic data manipulation verbs of dplyr, we’ll use nycflights13::flights. This data frame contains all 336,776 flights that departed from New York City in 2013. The data comes from the US Bureau of Transportation Statistics, and is documented in ?flights.

```{r, message=FALSE}
if (!require(nycflights13)) {
  install.packages("nycflights13",repos = "http://cran.us.r-project.org")
  library(nycflights13)
}
library(dplyr)

flights
```

`filter()` allows you to subset observations based on their values. The first argument is the name of the data frame. The second and subsequent arguments are the expressions that filter the data frame. For example, we can select all flights on January 1st with:

```{r}
filter(flights, month == 1, day == 1)
```

```{r, eval = TRUE}
numbers <- 1:1000

# This will print the first 10 elements of the vector numbers
numbers[1:10]

# This will plot a histogram of 100 random elements of the vector numbers
hist(sample(numbers, 100, replace = T))
```

...